\textbf{{\Large {Recursive algorithms, branching coefficients affine algebras and applications}}}

### 2010-01-01 AffineLieAlgebras/InformalNotes/article.tex
Preprint number added
Misspelling fixed
Added V.D. notes

\documentclass[a4paper,12pt]{article}
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm} 
\usepackage{pb-diagram}
\usepackage{ucs}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage[pdftex]{graphicx}
\pagestyle{plain}
\theoremstyle{definition} \newtheorem{Def}{Definition}

@@

\begin{center}
{\Large \bf SAINT-PETERSBURG STATE\\[0.5cm] UNIVERSITY}
\end{center}
\vskip 1 cm
\begin{flushright}
{\large \bf SPbU-IP-09-0?}
\end{flushright}
\hfill {}
\vskip 1 cm
\begin{center}
{\Huge \bf Recursive algorithms, branching coefficients \\ for affine algebras and applications\\[0.5cm]
}
\end{center}
\vskip 1.0 cm
\begin{center}
{\Large \bf
Vladimir Lyakhovsky\\[2mm]
Anton Nazarov}
\end{center}
\vfill
\begin{center}
{\large Department of Theoretical Physics\\
}
\end{center}
\vfill
\begin{center}
SAINT-PETERSBURG \\
2009
\end{center}

@@

We show that our algorithm can be used in a study of conformal embeddings where the central charge of the conformal field theory is preserved, and the computations are simplified taking into account some  physical limitations.

@@

Our aim is to demonstrate that despite possible singularities in the Weyl denominator projected to the subalgebra root space injection fan technique can be properly modified. as a result of such modification the generalized recurrent relations for anomalous branching coefficients \eqref{eq:21} will appear in the following form: 
\begin{equation}
  \label{eq:1}
  \begin{array}{c}
      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
\left.
+\sum_{\gamma \in
\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+\gamma }^{\left( \mu \right) }\right)
  \end{array}
   \end{equation}
Here $\mathfrak{a}_{\bot}$ is the subalgebra generated by the roots of $\mathfrak{g}$ orthogonal to the root system of $\mathfrak{a}$, $W_{\bot}$ is the corresponding Weyl group, $\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ is the set of weights in the expansion of the denominator $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$ and $s(\gamma)$ is the coefficient of $e^{\gamma}$ in this expansion.
In the next subsection we study the situation in details and prove the validity of this relation.

In the next section we  shall describe the  computational algorithm for  branching coefficients based on this formula and present some examples.

@@

The branching of a module can be symbolically written using formal characters and projection operators $\pi_{\mathfrak{a}}$ that bring the roots of $\mathfrak{g}$ to the weight subspace of $\mathfrak{a}$:
\begin{equation}
  \label{eq:3}
  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
  \Longrightarrow\quad
  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
\end{equation}
The Weyl-Kac character formula leads to
the equality
\begin{equation}
  \label{eq:4}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = 
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
\end{equation}

It is important to keep in mind that the projection of some of positive roots of the algebra $\mathfrak{g}$ can be equal to zero. These roots are orthogonal to the root space of the subalgebra $\mathfrak{a}$ embedded into the root space of the algebra $\mathfrak{g}$. Let's denote the subset of such roots by $\Delta^{+}_{\bot}=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.

@@

Now we should find out when the subset $\Delta^{+}_{\bot}$ is non-empty and the subgroup $W_{\bot}$ and subalgebra $\mathfrak{a}_{\bot}$ are non-trivial.

@@

The extended Dynkin diagram of $B_2$ is presented in the Figure \ref{fig:B2Dynkin}.
\begin{figure}[ph]
  \centering
  \includegraphics[width=50mm]{B2_A1_diagram.pdf}
  \caption{Extended Dynkin diagram of $B_2$ and embedding of $A_1$}
  \label{fig:B2Dynkin}
\end{figure}
When we drop the central node and get the embedding $A_1\oplus A_1\subset B_2$. Then $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.

Here we present the simple criterion of $\Delta^{+}_{\bot}$'s non-emptiness for a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ when both $\mathfrak{a}$ and $\mathfrak{g}$ are simple. If the Dynkin diagram of $\mathfrak{g}$ can be split into the disconnected diagrams of $\mathfrak{a}$ and some other subalgebras $\{\mathfrak{\bar{a}}_j\}$ then the subset $\Delta_{\bot}$ is non-empty, subalgebra $\mathfrak{a}_{\bot}$ is non-trivial and all the $\mathfrak{\bar{a}}_j$ are the subalgebras of $\mathfrak{a}_{\bot}$.

Note that when we study the regular embedding obtained by dropping the nodes of the extended Dynkin diagram of the algebra $\mathfrak{g}$ and the subalgebra $\mathfrak{a}$ is one of the connected components, the subalgebra $\mathfrak{a}_{\bot}$ may be broader than the algebra generated by the other connected components. See for example the figure \ref{fig:dynkin} for the embedding of $B_2\subset B_4$. 
In this case the extended Dynkin diagram of $B_4$ is split by dropping the simple root $\alpha_2=e_2-e_3$ into the diagrams of the subalgebra of interest $\mathfrak{a}=B_2$ and two diagrams of the orthogonal $A_1$ subalgebras. But the subalgebra $\mathfrak{a}_{\bot}$ is equal not to $A_1\oplus A_1$ but to $B_2$. 
This fact is due to the existence of the positive root $e_2=s_{\alpha_2}\cdot s_{\alpha_3}\cdot\alpha_4$ in the root system of $B_4$.

We should analyze the case when the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a subdiagram of the extended Dynkin diagram $\mathfrak{g}$ for the simple Lie algebras $\mathfrak{a},\,\mathfrak{g}$ and the regular embedding $\mathfrak{a}\subset \mathfrak{g}$.
 We drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with all the rest nodes of the diagram of $\mathfrak{g}$ and consider the remaining diagram. This diagram is the diagram of the algebra $\mathfrak{\bar{a}}$ of $\mathrm{rank}(\mathfrak{\bar{a}}) = \mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$. It is clear that $\mathfrak{\bar{a}}\subset \mathfrak{a}_{\bot}$. So the question is if $\mathfrak{a}_{\bot}$ has additional roots, which are not the roots of $\mathfrak{\bar{a}}$ but are the linear combinations of them. It is possible when the set of angles between the roots of $\mathfrak{\bar{a}}$ does not contain all the angles between the roots of $\mathfrak{a}$, then reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional roots of $\mathfrak{a}_{\bot}$.

@@

The exceptional Lie algebras require tedious case-by-case analysis.

In terms of Weyl groups the task of construction of the root system of $\mathfrak{a}_{\bot}$ is formulated as follows. Given a Weyl group $W$ and a subgroup $W_{\mathfrak{a}}$ find the subgroup $W_{\mathfrak{a}_{\bot}}\subset W$ such that $\omega\, W_{\mathfrak{a}}\,\omega^{-1}=W_{\mathfrak{a}}; \;\text{for}\; \omega\in W_{\mathfrak{a}_{\bot}}$, so we need to find the normalizer of $W_{\mathfrak{a}}$ in $W$, such that some of the elements of $W_{\mathfrak{a}_{\bot}}$ are the reflections corresponding to the positive roots of $\mathfrak{g}$. This task can be carried out using the computational methods of finite group theory \cite{stembridge2001computational} but we are unaware of any publication with the exhaustive tables of such subgroups.

In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the 
special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted at the Figure \ref{fig:a1a2a3}.
\begin{figure}[ph]
\noindent  \centering{
  \includegraphics[width=120mm]{special_A1_A2_A3.pdf}
  \caption{Special embedding $A_1\subset A_2\subset A_3$. Grey vectors are the roots of $A_2$, thick black - of $\mathfrak{a}=A_1$, dashed black are the orthogonal roots of $A_1$ which is contained in $\mathfrak{a}_{\bot}$ }
}
  \label{fig:a1a2a3}
\end{figure}

Using the existing classification of maximal special subalgebras \cite{dynkin1952semisimple} we immediately have the following pairs of the orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$ 
\begin{equation}
  \label{eq:42}
  \begin{array}{lll}
      su(p)\oplus su(q) & \subset su(pq) &\\
      so(p)\oplus so(q) & \subset so(pq) &\\
      sp(2p)\oplus sp(2q) & \subset so(4pq)&\\
      sp(2p)\oplus so(q) & \subset sp(2pq)&\\
      so(p)\oplus so(q) & \subset so(p+q)& \text{for}\;p\;\text{and}\;q\;\text{odd}\\
  \end{array}
\end{equation}
Exceptional Lie algebras and other non-maximal subalgebras require lengthy analysis which is not important for the needs of computation of the branching coefficients.

The construction of the subalgebra $\mathfrak{a}_{\bot}$ is not obvious from the Dynkin diagrams of $\mathfrak{g}$ and $\mathfrak{a}$ but for the needs of calculation of the branching coefficients $b^{(\mu)}_{\nu}$ it is sufficient to select the positive roots $\Delta^{+}_{\bot}=\left\{\alpha\in \Delta^{+}:\alpha\bot \Delta_{\mathfrak{a}}\right\}$ in the set of positive roots of $\mathfrak{g}$.

Now we look at the $\mathfrak{a}_{\bot}\oplus\mathfrak{h}$-module with the highest weight $\mu$. For the character of this module we get
\begin{equation}
  \label{eq:41}
  ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}= \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega) e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}
\end{equation}

If we consider the projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$ it will give us the single exponent $e^{\pi_{\mathfrak{a}}\cdot\mu}$ with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to the root system of $\mathfrak{a}$.

Using this idea we reorganize the expression for the character of $\mathfrak{g}$-module into the sum over $\mathfrak{a}_{\bot}\oplus\mathfrak{h}$-modules in the following way.

We can multiply the equation (\ref{eq:4}) by the term
\begin{equation}
  \label{eq:5}
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
\end{equation}
This term is non-zero.

Also we can see that for any formal polynomial or series $Q$
\begin{equation}
  \label{eq:6}
  \pi_{\mathfrak{a}} (Q) \pi_{\mathfrak{a}}(1-e^{-\alpha})=\pi_{\mathfrak{a}}\left(Q\cdot (1-e^{-\alpha})\right)
\end{equation}

The equation (\ref{eq:4}) takes the form
\begin{multline}
  \label{eq:7}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
\end{multline}
The right-hand side of this equation can be reorganised as in the paper \cite{ilyin812pbc}. We introduce the anomalous branching coefficients $k_{\lambda}$.
\begin{equation}
  \label{eq:10}
  \sum_{\nu \in P_{\frak{a}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
  }^{\left( \mu \right) }e^{\lambda } 
\end{equation}
Also we extract the common denominator of  the right-hand side of the equation (\ref{eq:7})
\begin{multline}
  \label{eq:12}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{\alpha}}} \right)
    \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda } 
\end{multline}

If the set $\Delta^{+}_{\bot}$ is non-empty then the Weyl reflections corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}$ of Weyl group $W$.

We have denoted the subalgebra with the root space spanned over the set $\Delta^{+}_{\bot}$ by $\mathfrak{a}_{\bot}$.

>>>>

\documentclass[a4paper,12pt]{article}
\usepackage[unicode,verbose]{hyperref}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{pb-diagram}
\usepackage{ucs}
%\usepackage[utf8x]{inputenc}
%\usepackage[russian]{babel}
\usepackage{cmap}
\usepackage{color}
\usepackage[pdftex]{graphicx}
\pagestyle{plain}
\theoremstyle{definition} \newtheorem{Def}{Definition}

@@

\begin{center}
{\Large \bf SAINT-PETERSBURG STATE\\[0.5cm] UNIVERSITY}
\end{center}
\vskip 1 cm
\begin{flushright}
{\large \bf SPbU-IP-09-08}
\end{flushright}
\hfill {}
\vskip 1 cm
\begin{center}
{\Huge \bf Recursive algorithms, branching coefficients \\ for affine algebras and applications\\[0.5cm]
}
\end{center}
\vskip 1.0 cm
\begin{center}
{\Large \bf
Vladimir Lyakhovsky\\[2mm]
Anton Nazarov}
\end{center}
\vfill
\begin{center}
{\large Department of Theoretical Physics\\
}
\end{center}
\vfill
\begin{center}
SAINT-PETERSBURG \\
2009
\end{center}

@@

We show that our algorithm can be used in a study of conformal embeddings where the central charge of the conformal field theory is preserved, and the computations are simplified by taking into account some  physical limitations.

@@

Our aim is to demonstrate that despite possible singularities arriving in the Weyl denominator
when it is projected to the subalgebra root space injection fan technique can be properly modified.
The result of such modification is that the generalized recurrent relations for anomalous branching
coefficients \eqref{eq:21} must be reformulated in the following form:
\begin{equation}
  \label{eq:1}
  \begin{array}{c}
      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
\left.
+\sum_{\gamma \in
\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+\gamma }^{\left( \mu \right) }\right)
  \end{array}
   \end{equation}
Here $\mathfrak{a}_{\bot}$ is the subalgebra described by the roots of $\mathfrak{g}$
orthogonal to the root subsystem of $\mathfrak{a}$, $W_{\bot}$ is the corresponding Weyl group,
$\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ is the set of weights in the expansion
of the denominator $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}
(1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$ and $s(\gamma)$
is the coefficient of $e^{\gamma}$ in this expansion.
In the next subsection we study the situation in details and prove the validity of this relation.

In the section \ref{sec:algorithm} we  shall describe the  computational algorithm for  branching coefficients
based on this formula and present some examples.

@@

Consider the branching of a module $L_{\frak{g}}^{\mu }$ in terms of formal characters and
projection operators $\pi_{\mathfrak{a}}$ that bring the roots of $\mathfrak{g}$ to the
weight subspace of $\mathfrak{a}$:
\begin{equation}
  \label{eq:3}
  L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
    }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
  \Longrightarrow\quad
  \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}
\end{equation}
The Weyl-Kac character formula leads to
the equality
\begin{equation}
  \label{eq:4}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
  {\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) =
  \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)
  e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
  {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
\end{equation}

It is important to keep in mind that the projection of some of positive roots of
the algebra $\mathfrak{g}$ can be equal to zero. These roots are orthogonal to the
root space of the subalgebra $\mathfrak{a}$ embedded into the root space of the
algebra $\mathfrak{g}$. Let's denote the subset of such roots by $\Delta^{+}_{\bot}
=\left\{\alpha\in\Delta_{\mathfrak{g}}^{+}:
\forall \beta\in \Delta_{\mathfrak{a}}^{+},\; \alpha\bot\beta \right\}$.

@@

Now we are to find out when the subset $\Delta^{+}_{\bot}$ is non-empty
and the subgroup $W_{\bot}$ and subalgebra $\mathfrak{a}_{\bot}$ are non-trivial.

@@

The extended Dynkin diagram of $B_2$ is presented in the Figure \ref{fig:B2Dynkin}.
\begin{figure}[ph]
  \centering
  \includegraphics[width=50mm]{B2_A1_diagram.pdf}
  \caption{Extended Dynkin diagram of $B_2$ and embedding of $A_1$}
  \label{fig:B2Dynkin}
\end{figure}
Drop the central node to describe the embedding $A_1\oplus A_1\subset B_2$.
In this case we have: $\mathfrak{a}=A_1$ and $\mathfrak{a}_{\bot}=A_1$.

The simple criterion of $\Delta^{+}_{\bot}$'s non-emptiness for a regular
embedding $\mathfrak{a}\subset \mathfrak{g}$
when both $\mathfrak{a}$ and $\mathfrak{g}$ are simple can be formulated
as follows:
if the Dynkin diagram of $\mathfrak{g}$ can be split into the disconnected
diagrams of $\mathfrak{a}$ and of some subalgebras $\{\mathfrak{\bar{a}}_j\}$
then the subset $\Delta_{\bot}$ is non-empty,
subalgebra $\mathfrak{a}_{\bot}$ is non-trivial and all the
$\mathfrak{\bar{a}}_j$ are the subalgebras of $\mathfrak{a}_{\bot}$.

Note that when we study the regular embedding obtained by dropping the nodes
of the extended Dynkin diagram of the algebra $\mathfrak{g}$ and the
subalgebra $\mathfrak{a}$ is one of the connected components,
the subalgebra $\mathfrak{a}_{\bot}$ may be larger than the algebra
generated by the remaining connected components.
Consider for example the embedding of $B_2\subset B_4$ (the figure \ref{fig:dynkin}).
In this case by eliminating
the simple root $\alpha_2=e_2-e_3$ one splits the extended Dynkin diagram of $B_4$
into the diagrams of the subalgebra $\mathfrak{a}=B_2$ and that of the direct
sum $A_1 \oplus A_1 $. But the subalgebra $\mathfrak{a}_{\bot}$ is equal not to
$A_1\oplus A_1$ but to $B_2$ (the root system of $B_4$ contains not only $\alpha_2=e_2-e_3$ but also $e_2$).

Such effects are due to the fact that the subalgebras $\mathfrak{a}$ and $\mathfrak{a}_{\bot}$ must not form a direct sum in $\mathfrak{g}$.  
Consider the case of such a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ where both algebras are simple and the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a subdiagram of the extended Dynkin diagram $\mathfrak{g}$.
 Drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with all the remaining nodes of the diagram of $\mathfrak{g}$. Consider the remaining diagram. This diagram is the diagram of the algebra $\mathfrak{\bar{a}}$ of $\mathrm{rank}(\mathfrak{\bar{a}}) = \mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$. It is clear that $\mathfrak{\bar{a}}\subset \mathfrak{a}_{\bot}$. So the question is whether $\mathfrak{a}_{\bot}$ has additional roots, which are not the roots of $\mathfrak{\bar{a}}$ but are the linear combinations of them. It is possible when the set of angles between the roots of $\mathfrak{\bar{a}}$ does not contain all the angles between the roots of $\mathfrak{a}$, then reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional roots of $\mathfrak{a}_{\bot}$.

@@

In Weyl group terms to construct $\Delta _{\mathfrak{a}_{\bot}} $ means the following: given a Weyl group $W$ and a subgroup $W_{\mathfrak{a}}$ find the subgroup $W_{\mathfrak{a}_{\bot}}\subset W$ such that $\omega\, W_{\mathfrak{a}}\,\omega^{-1}=W_{\mathfrak{a}} \;\text{for}\; \omega\in W_{\mathfrak{a}_{\bot}}$, so we need to find the normalizer {\color{red} (not the centralizer?, no proof)} of $W_{\mathfrak{a}}$ in $W$, (such that some of the elements of $W_{\mathfrak{a}_{\bot}}$ are the reflections corresponding to the positive roots of $\mathfrak{g}$  {\color{red}(?) and if so where is the proof?}). This task can be carried out using the computational methods of finite group theory \cite{stembridge2001computational} (but we are unaware of any publication with the exhaustive tables of such subgroups {\color{red}(drop it in the final text?)}).

(In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the
special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted at the Figure \ref{fig:a1a2a3}. {\color{red}(This is for us!)})
\begin{figure}[ph]
\noindent  \centering{
  \includegraphics[width=120mm]{special_A1_A2_A3.pdf}
  \caption{Special embedding $A_1\subset A_2\subset A_3$. Grey vectors are the roots of $A_2$, thick black - of $\mathfrak{a}=A_1$, dashed black are the orthogonal roots of $A_1$ which is contained in $\mathfrak{a}_{\bot}$ }
}
  \label{fig:a1a2a3}
\end{figure}

Using the existing classification of maximal special subalgebras \cite{dynkin1952semisimple} we immediately have the following pairs of the orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$
\begin{equation}
  \label{eq:42}
  \begin{array}{lll}
      su(p)\oplus su(q) & \subset su(pq) &\\
      so(p)\oplus so(q) & \subset so(pq) &\\
      sp(2p)\oplus sp(2q) & \subset so(4pq)&\\
      sp(2p)\oplus so(q) & \subset sp(2pq)&\\
      so(p)\oplus so(q) & \subset so(p+q)& \text{for}\;p\;\text{and}\;q\;\text{odd}\\
  \end{array}
\end{equation}
{\color{blue} Exceptional Lie algebras and other non-maximal subalgebras will be considered elsewhere.}

{\color{blue} Up to this point we considered the problem of $\mathfrak{a}_{\bot}$-construction given $\mathfrak{a}\in\mathfrak{g}$ for regular injections in terms of Dynkin diagrams. When the root systems $ \Delta$ and $\Delta_{\mathfrak{a}}$ are known explicitly all that we need is to select the roots  
$\Delta_{\bot}=\left\{\alpha\in \Delta:\alpha\bot \Delta_{\mathfrak{a}}\right\}$ and correspondingly the positive roots
$\Delta^{+}_{\bot}=\left\{\alpha\in \Delta^{+}:\alpha\bot \Delta_{\mathfrak{a}}\right\}$. }

Now consider the $\mathfrak{a}_{\bot}\oplus\mathfrak{h}$-module 
{\color{red} What is $\mathfrak{h}$? If it is the Cartan of $\mathfrak{g}$ then there are too many Cartans! It must be $\mathfrak{h}_{\mathfrak{a}}$.}
with the highest weight $\mu$. For the character of this module we have
\begin{equation}
  \label{eq:41}
  ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}= \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega) e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}
\end{equation}
If we perform the projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$ this will give us the single element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$ with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$, since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.

Using this property we can reconsider the expression for the $\mathfrak{g}$-module character as the character of the direct sum of $\mathfrak{a}_{\bot}\oplus\mathfrak{h}$-modules.
Multiply the equation (\ref{eq:4}) by the element
\begin{equation}
  \label{eq:5}
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
\end{equation}
{\color{red}(This term is non-zero.) --This is for us.}
{\color{blue}Taking into account that for any formal series $Q$ and the polynomial the projection commutes with the multiplication,
\begin{equation}
  \label{eq:6}
  \pi_{\mathfrak{a}} (Q) \pi_{\mathfrak{a}}(1-e^{-\alpha})=\pi_{\mathfrak{a}}\left(Q\cdot (1-e^{-\alpha})\right),
\end{equation}
we can rewrite the 
the product of (\ref{eq:4}) and (\ref{eq:5}) in the form:}
\begin{multline}
  \label{eq:7}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
  \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
  \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}
\end{multline}
The right-hand side of this equation can be reorganised similarly to what was performed in the paper \cite{ilyin812pbc}. Introduce the anomalous branching coefficients $k_{\lambda}$.
\begin{equation}
  \label{eq:10}
  \sum_{\nu \in P_{\frak{a}}}b_{\nu }^{\left( \mu \right) }\Psi _{\left( \frak{%
        a}\right) }^{\left( \nu \right) }=\sum_{\lambda \in P_{\frak{a}}}k_{\lambda
  }^{\left( \mu \right) }e^{\lambda }
\end{equation}
and cancel the denominator in the right-hand side of the equation (\ref{eq:7})
\begin{multline}
  \label{eq:12}
  \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
  \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{a}}(\alpha)} \right)
    \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }
\end{multline}

If the set $\Delta^{+}_{\bot}$ is non-empty then the Weyl reflections corresponding to the positive roots of $\Delta^{+}_{\bot}$ generate a subgroup $W_{\bot}$ of the Weyl group $W$.
{\color{red} (We have denoted the subalgebra with the root space spanned over the set $\Delta^{+}_{\bot}$ by $\mathfrak{a}_{\bot}$) we are well acquainted with this!}
